Taking Dyads Seriously

### 2021-01-04 paper/5_concl.tex

International relations is about the interactions, relationships, and dependencies among countries or other important international actors. This is particularly true of scholarship in the tradition of the Correlates of War Project, but it is by no means limited to it.\footnote{See \cite{singer:1972} for an early description of the project and also see the project's Web site for an history and more recent efforts \url{http://www.correlatesofwar.org/}.} Many scholars have debated the use and abuse of dyadic data.\footnote{One recent on-line symposium can be found at \url{http://bit.ly/2wB2hab}.} A broad survey of the IR literature makes it clear that scholars find dyadic data to be an essential touchstone in the study of international relations \citep{erikson:pinto:2014,aronow:etal:2015}. \textcolor{blue}{Our findings bolster a growing recognition in the field of International Relations that interdependence plays an important role not just in terms of statistical estimations, but in the ways that scholars theorize about internationally relevant politics. Scholars have demonstrated the theoretical importance of interdependence through research on conflict \citep{dorff:etal:2020}, economic interdependence \citep{maoz:2009a}, and international treaties \citep{kinne:2013} among other topics.}

>>>>

International relations is about the interactions, relationships, and dependencies among countries or other important international actors. This is particularly true of scholarship in the tradition of the Correlates of War Project, but it is by no means limited to it.\footnote{See \cite{singer:1972} for an early description of the project and also see the project's Web site for an history and more recent efforts \url{http://www.correlatesofwar.org/}.} Many scholars have debated the use and abuse of dyadic data.\footnote{One recent on-line symposium can be found at \url{http://bit.ly/2wB2hab}.} A broad survey of the IR literature makes it clear that scholars find dyadic data to be an essential touchstone in the study of international relations \citep{erikson:pinto:2014,aronow:etal:2015}. Our findings bolster a growing recognition in the field of International Relations that interdependence influences not only statistical estimations, but how scholars theorize about internationally relevant politics. Scholars have demonstrated the theoretical importance of interdependence through research on intrastate conflict \citep{dorff:etal:2020}, interstate bargaining \citep{gallop:2017}, economic interdependence \citep{maoz:2009a}, and international treaties \citep{kinne:2013} among other topics.
